### 2021-04-16 input/background.tex
Split section into 2 sections: 1 only about broacast, 1 related work at the end

\section{Background and motivation}
\label{sec:background}

\TODO{More related work. More motivations etc. Maybe describe IPFS?}

%% \begin{definition}[Dynamic optimal partitioning]
%%   A dynamic optimal partitioning is an optimal partitioning where the
%%   set of sources $S$ does not monotonically increase. We suffix this
%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
%%   of sources by \underline{a}dding its partition with messages
%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
%%   leaves the set of sources by \underline{d}eleting its partition with
%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
%% \end{definition}

%% Unfortunately, due to differences in receipt order of messages between
%% processes, stale information may stop prematurely the propagation of
%% relevant messages leading to inconsistent partitioning.
%% \TODO{Figure~\ref{fig:del} shows that.}

One could solve this issue by using a conflict-free replicated data
type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
require eventual delivery of messages to ensure convergence. All
processes need to receive, deliver, hence broadcast all
operations. Some processes may receive operations unnecessary to their
correct functioning, for these operations did not happen in their
locality.  One could also solve this issue by removing partitions that
were not advertised for a defined
time~\cite{hemmati2015namebased}. \TODO{check distance-vector
  protocols.} However, relying on physical timeout could lead to
either premature removals of partitions when they are still operating;
or slow convergence where processes believe they belong to a partition
that was removed (\TODO{plot ?}). In addition, since timeouts imply a
continuous maintenance of partitions, such partitioning protocol
incurs an overhead even in quiet contexts without dynamic partitions.

%% \begin{problem}[\label{prob:intra}Consistent partitioning]
%%   How to enable \emph{consistent} dynamic optimal partitioning in
%%   dynamic network using scoped flooding?
%% \end{problem}

% \TODO{Dynamic Multiple-sources All-destinations shortest path on
%  dynamic graphs?}

%% \begin{figure}
%%   \begin{center}
%%     \input{input/figASmotivation.tex}
%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
%%       objects, processes do not know about all partitions that exist
%%       in the whole distributed system.}
%%   \end{center}
%% \end{figure}

%% To further improve scoped flooding in autonomous systems, processes
%% may belong to multiple partitions representing the objects they are
%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
%% nature of autonomous systems. Autonomous systems have topological
%% properties~\cite{nur2018geography} that processes can leverage to
%% avoid flooding the whole systems with control information about all
%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
%% partition about a specific object, flooding Paris's AS to notify
%% neighboring processes of the object. However, it does not flood the
%% whole network, for control information stops at Process $b$. It
%% significantly saves bandwidth compared to broadcast since processes
%% below entrypoints of autonomous systems are order of magnitude more
%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
%% to return an object they are unaware of. Processes remain efficient in
%% answering requests. \TODO{which is important for end users \REF.}

%% \begin{definition}[Partitions in asynchronous systems]
%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
%%   \TODO{TODO} \TODO{or multi-partitioning?}
%% \end{definition}

%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
%%   How to enable scoped flooding of objects in autonomous systems?
%% \end{problem}

%% Next Section presents our approach that solves these scientific
%% problems by relying on logical control information only.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

>>>>

\section{Background and Problem Definiton}
\label{sec:background}

Numerous studies exist on content indexing, either being centralized or distributed (see Section\ref{related_work}). In this paper
we advocate solutions that do not rely on requesting any remote entity before being able to access a given content. 
Indeed, in the Fog context, requesting a remote node before accessing any content has many drawbacks as previsoulsy explained.
This section thus focus on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
We explain why existing implementations are costly thus preventing their deployment in real systems.
Then, we describe the problem tackled by this paper at an abstract level to underline the challenges that drove the design of our proposal.

\subsection*{Disseminate localization information}
Enabling the accessibility of content without prior requests implies that the information about replica localization has to be pushed directly to the nodes.
Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}. Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node. Moreover, removing the lookup latency directly involves faster downloading times. 
Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
That means information that might only interests a small subset of nodes is actually spread out all over the network.

\subsection*{Locking down the dissemination}
To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level. 
Suppose there exists an oracle in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas. In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system. Equipped with these two information, it is then trivial for this oracle to compute for each node, where resides its closest replica for a given content. Mapping each node of the topology to a single replica amounts to partition the set of all nodes into $k$ disjoint sets (or partitions), where $k$ is the number of current replicas. Thus, every node in the same partition would get the content from the same replica. Interestingly, this partitioning matches the physical topology as neighbors physically closed in the infrastructure will most likely reside in the same partition.
For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event). 
The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).

Finally, we emphasize that information about a given replica localization should remain in a given geographical scope. 
Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.
This prevents the use of gossip protocols for example.  Indeed, gossip protocols are also appealing candidates to disseminate information reliably across a network~\cite{epidemic-protocol} and numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
However, these protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information. This implies that nodes will exchange messages with random nodes in the system far exceeding the geograhical scope.
